\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\usepackage{ulem}
\usepackage{xcolor}
\usepackage{color,array}

\begin{document}

\title{SE 3XA3: Problem Statement\\Spaceshooter Remix}

\author{Team \# 4, IRS Development 
		\\ Ibrahim Malik maliki2
		\\ Ryan Schnekenburger  schneker
		\\ Saad Khan khans126
}

\date{}

\maketitle

\newpage

\begin{table}[h]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 19, 2018 & Ibrahim Malik & Creation of Document\\
November 24, 2018 & Ibrahim Malik & Final changes for Rev1\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\noindent
\textbf{What is the problem that we are trying to solve?}
\smallskip
\\ \sout{There are several avenues of entertainment today and the average human now uses their computer to accomplish this along with their daily tasks.} \textcolor{red}{Computers can be used a variety of everyday tasks including entertainment.} While there are many video game developers and production companies that create content, our goal was to reimplement a modern version of a very classic game \textcolor{red}{called Spaceshooter}  that an average computer user can enjoy on their local machines. This game was previously available for certain machines only with an appropriate set of prerequisites. We will create a version of the game that shall be playable on most machines \sout{hopefully} and will allow the user to play a newer, cleaner version of the game with some \sout{exciting,} modern features.
\bigskip
\\ \textbf{Why is this an important problem?}
\smallskip
\\The original game is called Spaceshooters and is a very basic game that does not work correctly on all devices. \textcolor{red}{It was a very popular game in a 2D version in the early 1970s on handheld game consoles.} \sout{There are several versions of it that are available on different machines and} Different iterations of similar games are constantly played by many users around the world. However, as many other games have advanced in their complexity by offering various modern features, this game is still very primitive. It does not live up to the standards of this era and it reduces the chances of its replayability. An unreliable game will result in frustrations, errors and an overall negative experience. Hopefully, this project will alleviate some of those issues by providing a stable and exciting game that can bring back positive memories of his vintage game. 
\bigskip
\\ \textbf{What is the context of the problem we are solving?}
\smallskip
\\The stakeholders of this game are the computer players, group members/IRS developers, future developers and the TAs/Instructors of this course. This game should be playable by all ages on the local machine as long as they have access to it and a keyboard. Hence, the environment should be a free game that is played on their local desktop or laptop computers wherever they are situated. 

\end{document}

\wss{comment}

\ds{comment}

\mj{comment}

\cm{comment}

\mh{comment}

\end{document}